---
title: "Scraping_docs"
output: pdf_document
date: "2025-02-24"
author: "Alejandro Roemer & Hugo Salas, Github Test 2025"
This script helps us scrape all the docs we need from The American Presidency Project (TAPP). Specifically, all mentions of 'MEXICO', 'JAPAN', 'GERMANY', 'CANADA' and 'CHINA'. 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

### A. Retrieve the scraping functions we created

```{r}
set_wd_fn <- function(author){
  if (author == "Ale"){
    DATA_PATH <<- "~/My Drive/Desktop - Alejandro’s MacBook Air 2025/USMEX_TextAnalysis"
    UTILS_PATH <<- paste0(DATA_PATH, "/utils/")
    
  } else if (author == "Hugo"){
    DATA_PATH <<- "/Users/hugosalas/Roemer & Salas/data/"
    UTILS_PATH <<- "/Users/hugosalas/Roemer & Salas/USMEX_TextAnalysis/utils/"
  } 
  
  setwd(DATA_PATH)
}

set_wd_fn(author = "Ale")
source(paste0(UTILS_PATH, 'scraping_TAPP_utils.R'))
```

### B. First and most important search: Mexico mentions 
We scrape all articles containing the string "Mexico" and nott "New Mexico" or "Gulf of Mexico".

- **All of these Terms**: "Mexico"
- **Any of these Terms**:  
- **None of these Terms**: "Gulf of Mexico", "New Mexico"
- **Document Category**: All except for Timeline

```{r}
# Este es el URL con todas las categorias menos timeline
MEXICO_URL = "https://www.presidency.ucsb.edu/advanced-search?field-keywords=Mexico&field-keywords2=&field-keywords3=%22New+Mexico%22+%22Gulf+of+Mexico%22&from%5Bdate%5D=&to%5Bdate%5D=&person2=&category2%5B%5D=&category2%5B%5D=406&category2%5B%5D=83&category2%5B%5D=75&category2%5B%5D=55&category2%5B%5D=58&category2%5B%5D=74&category2%5B%5D=18&category2%5B%5D=76&category2%5B%5D=73&category2%5B%5D=69&category2%5B%5D=8&category2%5B%5D=78&category2%5B%5D=85&category2%5B%5D=52&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=82&category2%5B%5D=84&category2%5B%5D=51&category2%5B%5D=428&category2%5B%5D=59&category2%5B%5D=48&category2%5B%5D=54&category2%5B%5D=45&category2%5B%5D=400&category2%5B%5D=63&category2%5B%5D=65&category2%5B%5D=64&category2%5B%5D=49&category2%5B%5D=12&category2%5B%5D=77&category2%5B%5D=68&category2%5B%5D=407&category2%5B%5D=19&category2%5B%5D=408&category2%5B%5D=396&category2%5B%5D=81&category2%5B%5D=411&category2%5B%5D=66&category2%5B%5D=469&category2%5B%5D=57&category2%5B%5D=488&category2%5B%5D=456&category2%5B%5D=50&category2%5B%5D=442&category2%5B%5D=72&category2%5B%5D=382&category2%5B%5D=475&category2%5B%5D=476&category2%5B%5D=484&category2%5B%5D=383&category2%5B%5D=486&category2%5B%5D=70&category2%5B%5D=62&category2%5B%5D=80&category2%5B%5D=56&category2%5B%5D=71&category2%5B%5D=443&category2%5B%5D=10&category2%5B%5D=67&category2%5B%5D=16&category2%5B%5D=79&category2%5B%5D=17&category2%5B%5D=435&category2%5B%5D=13&category2%5B%5D=9&category2%5B%5D=14&category2%5B%5D=424&category2%5B%5D=423&items_per_page=25"

mexico_df = scrape_all_docs_from_URL(MEXICO_URL)
head(mexico_df)
save(mexico_df, file = str_c(DATA_PATH,"all_articles_MEXICO_df"))
```

### C. Additional searches: mention from top 5 trade partners
We scrape all articles that contain the name of one of US' top 5 trade partners (excluding Mexico).

- **All of these Terms**: China, Canada, Japan, Germany 
- **Any of these Terms**:  
- **None of these Terms**:
- **Document Category**: All except for Timeline

```{r}
CHINA_URL = "https://www.presidency.ucsb.edu/advanced-search?field-keywords=China&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&category2%5B%5D=&category2%5B%5D=406&category2%5B%5D=83&category2%5B%5D=75&category2%5B%5D=55&category2%5B%5D=58&category2%5B%5D=74&category2%5B%5D=18&category2%5B%5D=76&category2%5B%5D=73&category2%5B%5D=69&category2%5B%5D=8&category2%5B%5D=78&category2%5B%5D=85&category2%5B%5D=52&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=82&category2%5B%5D=84&category2%5B%5D=51&category2%5B%5D=428&category2%5B%5D=59&category2%5B%5D=48&category2%5B%5D=54&category2%5B%5D=45&category2%5B%5D=400&category2%5B%5D=63&category2%5B%5D=65&category2%5B%5D=64&category2%5B%5D=49&category2%5B%5D=12&category2%5B%5D=77&category2%5B%5D=68&category2%5B%5D=407&category2%5B%5D=19&category2%5B%5D=408&category2%5B%5D=396&category2%5B%5D=81&category2%5B%5D=411&category2%5B%5D=66&category2%5B%5D=469&category2%5B%5D=57&category2%5B%5D=488&category2%5B%5D=456&category2%5B%5D=50&category2%5B%5D=442&category2%5B%5D=72&category2%5B%5D=382&category2%5B%5D=475&category2%5B%5D=476&category2%5B%5D=484&category2%5B%5D=383&category2%5B%5D=486&category2%5B%5D=70&category2%5B%5D=62&category2%5B%5D=80&category2%5B%5D=56&category2%5B%5D=71&category2%5B%5D=443&category2%5B%5D=10&category2%5B%5D=67&category2%5B%5D=16&category2%5B%5D=79&category2%5B%5D=17&category2%5B%5D=435&category2%5B%5D=13&category2%5B%5D=9&category2%5B%5D=14&category2%5B%5D=424&category2%5B%5D=423&items_per_page=25"

CANADA_URL = "https://www.presidency.ucsb.edu/advanced-search?field-keywords=Canada&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&category2%5B%5D=&category2%5B%5D=406&category2%5B%5D=83&category2%5B%5D=75&category2%5B%5D=55&category2%5B%5D=58&category2%5B%5D=74&category2%5B%5D=18&category2%5B%5D=76&category2%5B%5D=73&category2%5B%5D=69&category2%5B%5D=8&category2%5B%5D=78&category2%5B%5D=85&category2%5B%5D=52&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=82&category2%5B%5D=84&category2%5B%5D=51&category2%5B%5D=428&category2%5B%5D=59&category2%5B%5D=48&category2%5B%5D=54&category2%5B%5D=45&category2%5B%5D=400&category2%5B%5D=63&category2%5B%5D=65&category2%5B%5D=64&category2%5B%5D=49&category2%5B%5D=12&category2%5B%5D=77&category2%5B%5D=68&category2%5B%5D=407&category2%5B%5D=19&category2%5B%5D=408&category2%5B%5D=396&category2%5B%5D=81&category2%5B%5D=411&category2%5B%5D=66&category2%5B%5D=469&category2%5B%5D=57&category2%5B%5D=488&category2%5B%5D=456&category2%5B%5D=50&category2%5B%5D=442&category2%5B%5D=72&category2%5B%5D=382&category2%5B%5D=475&category2%5B%5D=476&category2%5B%5D=484&category2%5B%5D=383&category2%5B%5D=486&category2%5B%5D=70&category2%5B%5D=62&category2%5B%5D=80&category2%5B%5D=56&category2%5B%5D=71&category2%5B%5D=443&category2%5B%5D=10&category2%5B%5D=67&category2%5B%5D=16&category2%5B%5D=79&category2%5B%5D=17&category2%5B%5D=435&category2%5B%5D=13&category2%5B%5D=9&category2%5B%5D=14&category2%5B%5D=424&category2%5B%5D=423&items_per_page=25"

JAPAN_URL = "https://www.presidency.ucsb.edu/advanced-search?field-keywords=Japan&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&category2%5B%5D=&category2%5B%5D=406&category2%5B%5D=83&category2%5B%5D=75&category2%5B%5D=55&category2%5B%5D=58&category2%5B%5D=74&category2%5B%5D=18&category2%5B%5D=76&category2%5B%5D=73&category2%5B%5D=69&category2%5B%5D=8&category2%5B%5D=78&category2%5B%5D=85&category2%5B%5D=52&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=82&category2%5B%5D=84&category2%5B%5D=51&category2%5B%5D=428&category2%5B%5D=59&category2%5B%5D=48&category2%5B%5D=54&category2%5B%5D=45&category2%5B%5D=400&category2%5B%5D=63&category2%5B%5D=65&category2%5B%5D=64&category2%5B%5D=49&category2%5B%5D=12&category2%5B%5D=77&category2%5B%5D=68&category2%5B%5D=407&category2%5B%5D=19&category2%5B%5D=408&category2%5B%5D=396&category2%5B%5D=81&category2%5B%5D=411&category2%5B%5D=66&category2%5B%5D=469&category2%5B%5D=57&category2%5B%5D=488&category2%5B%5D=456&category2%5B%5D=50&category2%5B%5D=442&category2%5B%5D=72&category2%5B%5D=382&category2%5B%5D=475&category2%5B%5D=476&category2%5B%5D=484&category2%5B%5D=383&category2%5B%5D=486&category2%5B%5D=70&category2%5B%5D=62&category2%5B%5D=80&category2%5B%5D=56&category2%5B%5D=71&category2%5B%5D=443&category2%5B%5D=10&category2%5B%5D=67&category2%5B%5D=16&category2%5B%5D=79&category2%5B%5D=17&category2%5B%5D=435&category2%5B%5D=13&category2%5B%5D=9&category2%5B%5D=14&category2%5B%5D=424&category2%5B%5D=423&items_per_page=25"

GERMANY_URL = "https://www.presidency.ucsb.edu/advanced-search?field-keywords=Germany&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2=&category2%5B%5D=&category2%5B%5D=406&category2%5B%5D=83&category2%5B%5D=75&category2%5B%5D=55&category2%5B%5D=58&category2%5B%5D=74&category2%5B%5D=18&category2%5B%5D=76&category2%5B%5D=73&category2%5B%5D=69&category2%5B%5D=8&category2%5B%5D=78&category2%5B%5D=85&category2%5B%5D=52&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=82&category2%5B%5D=84&category2%5B%5D=51&category2%5B%5D=428&category2%5B%5D=59&category2%5B%5D=48&category2%5B%5D=54&category2%5B%5D=45&category2%5B%5D=400&category2%5B%5D=63&category2%5B%5D=65&category2%5B%5D=64&category2%5B%5D=49&category2%5B%5D=12&category2%5B%5D=77&category2%5B%5D=68&category2%5B%5D=407&category2%5B%5D=19&category2%5B%5D=408&category2%5B%5D=396&category2%5B%5D=81&category2%5B%5D=411&category2%5B%5D=66&category2%5B%5D=469&category2%5B%5D=57&category2%5B%5D=488&category2%5B%5D=456&category2%5B%5D=50&category2%5B%5D=442&category2%5B%5D=72&category2%5B%5D=382&category2%5B%5D=475&category2%5B%5D=476&category2%5B%5D=484&category2%5B%5D=383&category2%5B%5D=486&category2%5B%5D=70&category2%5B%5D=62&category2%5B%5D=80&category2%5B%5D=56&category2%5B%5D=71&category2%5B%5D=443&category2%5B%5D=10&category2%5B%5D=67&category2%5B%5D=16&category2%5B%5D=79&category2%5B%5D=17&category2%5B%5D=435&category2%5B%5D=13&category2%5B%5D=9&category2%5B%5D=14&category2%5B%5D=424&category2%5B%5D=423&items_per_page=25"

TRADE_PARTNERS_URL = list(CHINA = CHINA_URL, 
                          CANADA = CANADA_URL, 
                          JAPAN = JAPAN_URL, 
                          GERMANY = GERMANY_URL)
```

```{r}
for (i in seq_along(TRADE_PARTNERS_URL)){
  country_name = names(TRADE_PARTNERS_URL)[i]
  print(country_name)
  country_df = scrape_all_docs_from_URL( TRADE_PARTNERS_URL[[i]] )
  save(country_df, file = str_c(DATA_PATH,"all_articles_", country_name, "_df"))
}
```

### D. Grab total number of documents written by PRESIDENT

```{r}
BASE_URL_HEAD <- "https://www.presidency.ucsb.edu/advanced-search?field-keywords=&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2="
BASE_URL_TAIL <- "&category2%5B%5D=406&category2%5B%5D=83&category2%5B%5D=75&category2%5B%5D=55&category2%5B%5D=58&category2%5B%5D=74&category2%5B%5D=18&category2%5B%5D=76&category2%5B%5D=73&category2%5B%5D=69&category2%5B%5D=8&category2%5B%5D=78&category2%5B%5D=85&category2%5B%5D=52&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=82&category2%5B%5D=84&category2%5B%5D=51&category2%5B%5D=428&category2%5B%5D=59&category2%5B%5D=48&category2%5B%5D=54&category2%5B%5D=45&category2%5B%5D=400&category2%5B%5D=63&category2%5B%5D=65&category2%5B%5D=64&category2%5B%5D=49&category2%5B%5D=12&category2%5B%5D=77&category2%5B%5D=68&category2%5B%5D=407&category2%5B%5D=19&category2%5B%5D=408&category2%5B%5D=396&category2%5B%5D=81&category2%5B%5D=411&category2%5B%5D=66&category2%5B%5D=469&category2%5B%5D=57&category2%5B%5D=488&category2%5B%5D=456&category2%5B%5D=50&category2%5B%5D=442&category2%5B%5D=72&category2%5B%5D=382&category2%5B%5D=475&category2%5B%5D=476&category2%5B%5D=484&category2%5B%5D=383&category2%5B%5D=486&category2%5B%5D=70&category2%5B%5D=62&category2%5B%5D=80&category2%5B%5D=56&category2%5B%5D=71&category2%5B%5D=443&category2%5B%5D=10&category2%5B%5D=67&category2%5B%5D=16&category2%5B%5D=79&category2%5B%5D=17&category2%5B%5D=435&category2%5B%5D=13&category2%5B%5D=9&category2%5B%5D=14&category2%5B%5D=424&category2%5B%5D=423&items_per_page=25"
PRESIDENT_IDS <- 200257:200320
```

```{r}
links <- paste0(BASE_URL_HEAD, PRESIDENT_IDS, BASE_URL_TAIL)

# Create an empty data frame to store the results
all_articles_presidents_df <- data.frame(president = character(), records = numeric())

# Loop through each link and scrape the relevant information
for (link in links) {
  page <- read_html(link)
  
  # Extract the president's name from the page and remove the newline character
  president <- page %>% html_nodes(".odd .views-field-field-docs-person") %>% html_text() %>% gsub("\n", "", .)
  president <- gsub("^\\s+|\\s+$", "", president[1]) #remove whitespace
  
  # Extract the number of records found from the page and remove any non-numeric characters
  records <- retrieve_number_of_records(page)
  
  # Check if president and records are not empty before adding to the data frame
  if (!is.na(president) & !is.na(records) & president != "" & records != "") {
    # Add the results to the data frame
    all_articles_presidents_df <- rbind(all_articles_presidents_df, data.frame(president = president, records = records))
  }
}

save(all_articles_presidents_df, file = str_c(DATA_PATH,"/all_articles_presidents_df"))
```

### E. Grab total number of documents written by YEAR

```{r}
BASE_URL_HEAD <- "https://www.presidency.ucsb.edu/advanced-search?field-keywords=&field-keywords2=&field-keywords3=&from%5Bdate%5D=01-01-"
BASE_URL_BELLY <- "&to%5Bdate%5D=12-31-"
BASE_URL_TAIL <- "&person2=&category2%5B%5D=406&category2%5B%5D=83&category2%5B%5D=75&category2%5B%5D=55&category2%5B%5D=58&category2%5B%5D=74&category2%5B%5D=18&category2%5B%5D=76&category2%5B%5D=73&category2%5B%5D=69&category2%5B%5D=8&category2%5B%5D=78&category2%5B%5D=85&category2%5B%5D=52&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=82&category2%5B%5D=84&category2%5B%5D=51&category2%5B%5D=428&category2%5B%5D=59&category2%5B%5D=48&category2%5B%5D=54&category2%5B%5D=45&category2%5B%5D=400&category2%5B%5D=63&category2%5B%5D=65&category2%5B%5D=64&category2%5B%5D=49&category2%5B%5D=12&category2%5B%5D=77&category2%5B%5D=68&category2%5B%5D=407&category2%5B%5D=19&category2%5B%5D=408&category2%5B%5D=396&category2%5B%5D=81&category2%5B%5D=411&category2%5B%5D=66&category2%5B%5D=469&category2%5B%5D=57&category2%5B%5D=488&category2%5B%5D=456&category2%5B%5D=50&category2%5B%5D=442&category2%5B%5D=72&category2%5B%5D=382&category2%5B%5D=475&category2%5B%5D=476&category2%5B%5D=484&category2%5B%5D=383&category2%5B%5D=486&category2%5B%5D=70&category2%5B%5D=62&category2%5B%5D=80&category2%5B%5D=56&category2%5B%5D=71&category2%5B%5D=443&category2%5B%5D=10&category2%5B%5D=67&category2%5B%5D=16&category2%5B%5D=79&category2%5B%5D=17&category2%5B%5D=435&category2%5B%5D=13&category2%5B%5D=9&category2%5B%5D=14&category2%5B%5D=424&category2%5B%5D=423&items_per_page=25"
YEARS <- 1789:2024
```

```{r}
# Create an empty data frame to store the results
all_articles_years_df <- data.frame(year = numeric(), records = numeric())

# Loop through each link and scrape the relevant information
for (year in YEARS) {
  
  link <- paste0(BASE_URL_HEAD, year, BASE_URL_BELLY, year, BASE_URL_TAIL)
  page <- read_html(link)
  
  # Extract the number of records found from the page and remove any non-numeric characters
  records <- retrieve_number_of_records(page)
  
  # Check if president and records are not empty before adding to the data frame
  if (!is.na(year) & !is.na(records) & year != "" & records != "") {
    # Add the results to the data frame
    all_articles_years_df <- rbind(all_articles_years_df, data.frame(year = year, records = records))
  }
}

save(all_articles_years_df, file = str_c(DATA_PATH,"/all_articles_years_df"))
```