---
title: "cleaning_n_descriptive"
output: pdf_document
date: "2023-04-26"
author: "Alejandro Roemer & Hugo Salas"

This was originally 'preprocessing_usmex.rmd'. We create a series of graphs to describe our data.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### A. Load all relevant packages and set directories

```{r, message=FALSE, warning = FALSE}
require(quanteda)
require(quanteda.textmodels)
require(quanteda.textstats)
require(quanteda.textplots)
require(quanteda.corpora)

library(ggrepel)
library(readxl)
library(rvest)
require(readtext)
require(devtools)
require(tidyverse)
require(ggplot2) 
library(stringr)
library(purrr)
library(readr)
library(lubridate)
library(scales)
```

```{r, message=FALSE, warning = FALSE}
rm(list = ls())

if (Sys.info()["user"]=='hugosalas'){
  BASE_PATH = "/Users/hugosalas/Roemer & Salas/"
} else if (Sys.info()["user"]=='aleroemer'){
  BASE_PATH = "~/My Drive/DiscursoUSA_MX/"
}

DATA_PATH =  paste0(BASE_PATH, "data/")
CLEAN_DATA_PATH = paste0(DATA_PATH, "clean/")
UTILS_PATH = paste0(BASE_PATH, "USMEX_TextAnalysis/utils/")

source(str_c(UTILS_PATH, 'data_manipulation_utils.R'))
```

### B. Load all relevant files and DF

```{r, message=FALSE}

## Article data from our 5 countries
FILES_TO_LOAD = c("all_articles_CANADA_df", "all_articles_JAPAN_df", 
                  "all_articles_GERMANY_df", "all_articles_CHINA_df", 
                  "all_articles_MEXICO_df", 'all_articles_presidents_df',
                  "all_articles_years_df")

# Store all dfs in a list
trade_partners_lst = list()

for (file in FILES_TO_LOAD){
  load(str_c(DATA_PATH , file))
  
  if (file != 'all_articles_presidents_df' &
      file != 'all_articles_years_df'){
    country_name = str_replace(file, "all_articles_", "")
    country_name = str_replace(country_name, "_df", "")
    
    if (file != "all_articles_MEXICO_df"){
      trade_partners_lst[[country_name]] = country_df
      rm(country_df)
    } else {
      trade_partners_lst[[country_name]] = mexico_df
      rm(mexico_df)
    }
  }
}

## Data at the president level with party membership, length of stay, among others
party_df <- read_csv(str_c(DATA_PATH, "presidents.csv"))
```

### C. Data cleaning and manipulation

```{r, message=FALSE}
# We remove certain categories that we don't find relevant for our analysis
CATEGORIES_TO_OMIT <- c("Vice Presidential", 
                        "Vice Presidential Candidates", 
                        "Vice President's Press Secretary", 
                        "Vice Presidential Debates", 
                        "Statements by the Vice President",
                        "Remarks by the Vice President", 
                        "First Lady's Press Secretary",
                        "First Lady")

## Clean the data we have on presidents
party_df = clean_party_df(party_df)

## Cleaning our doc data from all our countries
for (country in seq_along(trade_partners_lst)){
  # Reformat dates in all DFs so that they look intuitive
  trade_partners_lst[[ country ]]$date = as.Date(as.numeric(trade_partners_lst[[ country ]]$date))
  # Add last name and year to DF
  trade_partners_lst[[ country ]] = add_last_name_n_year_to_df( trade_partners_lst[[ country ]] )
  # Merge with party/president data
  trade_partners_lst[[ country ]] <- trade_partners_lst[[ country ]] %>% 
    inner_join(party_df, by = c("last_name" = "last_name"))
  # Recategorize party variable so it separates between democrats and republicans
  trade_partners_lst[[ country ]] <- recategorize_parties(trade_partners_lst[[ country ]])
  
  #Remove uninteresting categories
  for (category in CATEGORIES_TO_OMIT){
    trade_partners_lst[[ country ]] = trade_partners_lst[[ country ]][trade_partners_lst[[ country ]][category]==0,]
  }
}
```

### D. Quick data exploration to get some truths about each country

```{r, message=FALSE}
for (country in names(trade_partners_lst)){
  print(str_c('############## ', country, ' ############'))
  
  nrows = nrow( trade_partners_lst[[ country ]] )
  print(str_c('Number of rows/docs: ', nrows ))
  
  print('Party Membership %')
  print(table( trade_partners_lst[[ country ]]$Party)/nrows*100)
  
  print('Doc category % (top 7)')
  print(sort(colSums( trade_partners_lst[[ country ]][,5:74], na.rm = TRUE), decreasing = TRUE)[1:7]/nrows)
  
  print(str_c('Share of docs not coming directly from the president: ', sum(is.na(trade_partners_lst[[ country ]]$Party))/nrows*100))
  
  for (i in 1:3){
    cat("\n")
  }
}
```

### E. Mentions by year per country

```{r, warning=FALSE}
counts_year = data.frame()

for (country in seq_along(trade_partners_lst)){
  
  # Group by year while we count
  groupby_temp <- trade_partners_lst[[country]]%>% 
    group_by(year) %>% 
     summarise(n_docs = n()) 
  
  # Add a column to identify each batch/country
  groupby_temp['country'] = names(trade_partners_lst)[country]
  
  # Append to df
  counts_year = rbind(counts_year, groupby_temp)
}
# We remove 2024, since our latest data point is in Aug-18-2024
counts_year = counts_year[counts_year$year<2024,]
```

```{r, warning=FALSE}
# Let's create a label in spanish
counts_year <- counts_year %>%
  mutate(country_spanish = case_when(
    country == "CHINA" ~ "China",
    country == "CANADA" ~ "Canadá",
    country == "MEXICO" ~ "México",
    country == "JAPAN" ~ "Japón",
    country == "GERMANY" ~ "Alemania",
    TRUE ~ country  # Retain the original country name if it's not in the list
  ))
# Define your custom colors
custom_colors <- c(
  "China" = "#58508d",    # Red
  "Canadá" = "#bc5090",   # Blue
  "México" = "#003f5c",   # Green
  "Japón" = "#ff6361",    # Orange
  "Alemania" = "#ffa600"  # Purple
)
```

```{r, warning=FALSE}
# First time series: from 1800 to 1980
plot <- ggplot(counts_year[counts_year['year'] >= 1880 & counts_year['year'] < 1960, ], aes(year, n_docs, color = country_spanish)) + 
  geom_rect(aes(xmin = 1918, xmax = 1920, ymin = 0, ymax = 70),
            fill = "grey80", alpha = 0.02, color=NA) +
  geom_rect(aes(xmin = 1928, xmax = 1930, ymin = 0, ymax = 70),
            fill = "grey80", alpha = 0.02, color=NA) +
  geom_rect(aes(xmin = 1944, xmax = 1946, ymin = 0, ymax = 70),
            fill = "grey80", alpha = 0.02, color=NA) +
  geom_line(aes(group = country_spanish), size = 0.75) +
  theme_test() +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(n = 5)) +
  theme(axis.text.x = element_text(angle = 0, vjust = .7)) +
  labs(title = '¿Cuánto Menciona EEUU a sus socios comerciales?',
       subtitle = "",
       y = "", 
       x = "", 
       caption = "",
       color = 'País') +  # Change the legend title to Spanish
  scale_color_manual(values = custom_colors)  # Apply custom colors

print(plot)
```

```{r, warning=FALSE}
# Second time series: from 1980 to 2023
plot <- ggplot(counts_year[counts_year['year'] > 1980, ], aes(year, n_docs, color = country_spanish)) + 
  geom_rect(aes(xmin = 1991, xmax = 1994, ymin = 0, ymax = 900),
            fill = "grey80", alpha = 0.02, color=NA) +
  geom_rect(aes(xmin = 2016, xmax = 2020, ymin = 0, ymax = 900),
            fill = "grey80", alpha = 0.02, color=NA) +
  geom_line(aes(group = country_spanish), size = 0.75) +
  theme_test() +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(n = 5)) +
  theme(axis.text.x = element_text(angle = 0, vjust = .7)) +
  labs(title = '¿Cuánto Menciona EEUU a sus socios comerciales?',
       subtitle = "",
       y = "", 
       x = "", 
       caption = "",
       color = 'País') +  # Change the legend title to Spanish
  scale_color_manual(values = custom_colors)  # Apply custom colors

print(plot)
```

```{r}
# Categorize years so that we can have a cleaner look
counts_year <- counts_year %>%
    mutate(year_category = case_when(
        year >= 1800 & year <= 1900 ~ '1800-1900',
        year >= 1901 & year <= 1950 ~ '1901-1950',
        year >= 1951 & year <= 2000 ~ '1951-2000',
        year >= 2001 & year <= 2020 ~ '2001-2020',
        TRUE ~ 'Outside Range'  # Optionally handle years outside these ranges
    ))
# Drop obs that do not fall within the established range
counts_year <- counts_year %>%
  filter(year_category != 'Outside Range')

# Get the total number of documents per year
counts_year = inner_join(all_articles_years_df, counts_year, by = "year")
counts_year$records <- as.numeric(counts_year$records)

# Group by our year categorization
counts_year_category <- counts_year %>%
  group_by(year_category, country_spanish) %>%
  summarize(total_docs_per_country = sum(n_docs),
            total_docs = sum(records))

# Make year_category so that they are ordered in the plot too
counts_year_category <- counts_year_category %>%
  mutate(year_category = factor(year_category, levels = c('2001-2020','1951-2000', '1901-1950', '1800-1900')))

# Create a ratio
counts_year_category$share_docs_per_country= counts_year_category$total_docs_per_country/counts_year_category$total_docs*100
```

```{r}
# Plot
ggplot(counts_year_category, aes(x = share_docs_per_country, y = year_category, fill = country_spanish)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("%.1f", share_docs_per_country)), 
            position = position_dodge(width = 0.9), 
            hjust = -0.2,  # Adjust position if needed
            size = 3.5) +  # Adjust text size if needed
  labs(x = "%", y = "", 
       title = "Porcentaje de referencias por país") +
  scale_fill_manual(name = "País", values = custom_colors) + 
  theme_minimal()
```

### F. Mexico mentions by year

#### i) Raw count

```{r, warning=FALSE}
Y_VAL = 200
COLOR = "#003f5c"
SIZE = 3
library(zoo)
counts_year_mexico = counts_year[counts_year$country=='MEXICO',]
counts_year_mexico$rolling_avg_n_docs <- rollmean(counts_year_mexico$n_docs, k = 3, fill = NA, align = "right")
counts_year_mexico %>% 
  ggplot(aes(x = year, y = rolling_avg_n_docs)) +
  geom_rect(aes(xmin = 1846, xmax = 1848, ymin = 0, ymax = 300),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 1864, xmax = 1867, ymin = 0, ymax = 300),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 1910, xmax = 1917, ymin = 0, ymax = 300),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 1991, xmax = 1994, ymin = 0, ymax = 300),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 2016, xmax = 2020, ymin = 0, ymax = 300),
            fill = "grey80", alpha = 0.02) +
  geom_line(color =COLOR) +
  theme_test() +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(n = 5)) +
  #ylim(0, NA) +
  labs(title = 'Documentos presidenciales con mención de "México" ',
       subtitle = "",
       y = "", 
       x = "", 
       caption = "*discursos disponibles en https://www.presidency.ucsb.edu/")

```

```{r, warning=FALSE}
Y_VAL = 200
COLOR = "blue"
SIZE = 3

counts_year[counts_year$country=='MEXICO',] %>% 
  ggplot(aes(x = year, y = n_docs)) +
  geom_line() +
  theme_test() +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(n = 5)) +
  geom_vline(aes(xintercept = 1847.5), linetype = "dotted", color = COLOR)+   
  annotate("text", x=1827, y=Y_VAL, label="1848 - Fin de Guerra \nMéxico-Americana ", color = COLOR, size = SIZE)+
  geom_vline(aes(xintercept = 1864), linetype = "dotted", color = COLOR)+   
  annotate("text", x=1876, y=Y_VAL, label="1862 - \nMaximiliano", color = COLOR, size = SIZE)+
   geom_vline(aes(xintercept = 1910), linetype = "dotted", color = COLOR)+   
  annotate("text", x=1920, y=Y_VAL, label="1910-1917 \nRevolución", color = COLOR, size = SIZE)+
  geom_vline(aes(xintercept = 1917), linetype = "dotted", color = COLOR)+ 
  #geom_vline(aes(xintercept = 1923), linetype = "dotted", color = COLOR) +   
  #annotate("text", x=1937, y=Y_VAL, label="1923 - \nSuspensión \nde relaciones \ndiplomáticas", color = COLOR, size = SIZE) +
  geom_vline(aes(xintercept = 1993), linetype = "dotted", color = COLOR) +   
  annotate("text", x=1985, y=Y_VAL, label="1993 - \nTLCAN", color = COLOR, size = SIZE) +
  geom_vline(aes(xintercept = 2017), linetype = "dotted", color = COLOR) +   
  annotate("text", x=2010, y=Y_VAL, label="2017 - \nTrump", color = COLOR, size = SIZE)+
  labs(title = 'Documentos presidenciales con mención de "México" ',
       subtitle = "",
       y = "", 
       x = "", 
       caption = "*discursos disponibles en https://www.presidency.ucsb.edu/")
```

#### ii) Normalized by total docs by year

```{r, warning=FALSE}
Y_VAL = 25

counts_year['share'] = counts_year$n_docs/as.integer(counts_year$records)*100
```

```{r, warning=FALSE}
COLOR = "#003f5c"
counts_year[counts_year$country=='MEXICO',] %>% 
  ggplot(aes(x = year, y = share)) +
  geom_rect(aes(xmin = 1846, xmax = 1848, ymin = 0, ymax = 30),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 1864, xmax = 1867, ymin = 0, ymax = 30),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 1910, xmax = 1917, ymin = 0, ymax = 30),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 1991, xmax = 1994, ymin = 0, ymax = 30),
            fill = "grey80", alpha = 0.02) +
  geom_rect(aes(xmin = 2016, xmax = 2020, ymin = 0, ymax = 30),
            fill = "grey80", alpha = 0.02) +
  geom_line(color=COLOR) +
  theme_test() +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(n = 5)) +
  geom_hline(yintercept = mean(counts_year[counts_year$country=='MEXICO','share']), color = 'black', linetype='dotted') +
  labs(title = 'Documentos presidenciales con mención de "México" ',
       subtitle = "Como % del total de documentos ese año",
       y = "%", 
       x = "", 
       caption = "*discursos disponibles en https://www.presidency.ucsb.edu/")

```

```{r, warning=FALSE}
counts_year[counts_year$country=='MEXICO',] %>% 
  ggplot(aes(x = year, y = share)) +
  geom_line() +
  theme_test() +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(n = 5)) +
  geom_hline(yintercept = mean(counts_year[counts_year$country=='MEXICO','share']), color = 'black', linetype='dotted') +
  geom_vline(aes(xintercept = 1847.5), linetype = "dotted", color = COLOR)+   
  annotate("text", x=1827, y=Y_VAL, label="1848 - Fin de Guerra \nMéxico-Americana ", color = COLOR, size = SIZE)+
  geom_vline(aes(xintercept = 1865), linetype = "dotted", color = COLOR)+   
  annotate("text", x=1876, y=Y_VAL, label="1862 - \nMaximiliano", color = COLOR, size = SIZE)+
  geom_vline(aes(xintercept = 1910), linetype = "dotted", color = COLOR)+   
  annotate("text", x=1920, y=Y_VAL, label="1910-1917 \nRevolución", color = COLOR, size = SIZE)+
   geom_vline(aes(xintercept = 1917), linetype = "dotted", color = COLOR)+   
  #geom_vline(aes(xintercept = 1923), linetype = "dotted", color = COLOR) +   
  #annotate("text", x=1945, y=Y_VAL, label="1923 - Suspensión \nrelaciones diplomáticas", color = COLOR, size = SIZE) +
  geom_vline(aes(xintercept = 1993), linetype = "dotted", color = COLOR) +   
  annotate("text", x=1985, y=Y_VAL, label="1993 - \nTLCAN", color = COLOR, size = SIZE) +
  geom_vline(aes(xintercept = 2017), linetype = "dotted", color = COLOR) +   
  annotate("text", x=2010, y=Y_VAL, label="2017 - \nTrump", color = COLOR, size = SIZE)+
  labs(title = 'Documentos presidenciales con mención de "México" ',
       subtitle = "Como % del total de documentos ese año",
       y = "%", 
       x = "", 
       caption = "*discursos disponibles en https://www.presidency.ucsb.edu/")

```

#### iii) Zooming in on NAFTA

```{r}
## Intentar de 92 a 95
mex_df_90s <- trade_partners_lst[["MEXICO"]] %>% 
  filter(format(date, "%Y") %in% c("1989","1990","1991","1992", "1993", "1994", "1995", "1996")) %>% 
  select(speaker, date, title, text)

# Create a new column called 'mentions_nafta' that indicates whether the speech mentions NAFTA, trade agreement, or Trade Agreement
mex_df_90s <- mex_df_90s %>% 
  mutate(mentions_nafta = ifelse(grepl("NAFTA|trade agreement|Trade Agreement", text), 1, 0),
         year = year(date))

totals_year <- mex_df_90s %>% 
  group_by(year) %>% 
  summarise(total = n())

nafta_summary <- mex_df_90s %>% 
  group_by(mentions_nafta, year) %>% 
  summarise(count = n()) %>% 
  left_join(totals_year, by = "year") %>% 
  mutate(percent = count / total*100)

ggplot(nafta_summary, aes(x = factor(year), y = count*100, fill = factor(mentions_nafta))) +
  geom_bar(position = "fill", stat = "identity") +
  #geom_text(aes(label = if_else(mentions_nafta == 1, percent, ""), y = percent, vjust = -1))
  #geom_text(aes(label = if_else(mentions_nafta == 1,
   #             round(percent,2), y = percent, ""), vjust = -1)) +
  labs(x = "", y = "", fill = "Menciona al TLCAN",
       title = "Porcentaje de textos que mencionan el TLCAN",

       caption = 'Términos consultados: "NAFTA" o "Trade Agreement"') +
  scale_fill_manual(values = c("0" = "#003f5c", "1" = "#ff6361"),
                    labels = c("1" = "Sí", "0" = "No")) +
  theme_minimal()
```

```{r}
nafta_summary[nafta_summary$mentions_nafta == 1, ]

```

### G. Mexico mentions by president

#### i) Raw count

```{r}
temp_df = trade_partners_lst$MEXICO

ndoc_pres <- temp_df %>% 
  group_by(last_name, speaker) %>% 
  summarise(n_docs = n()) %>% 
  arrange(desc(n_docs)) #hay que sacar a hillary clinton


# Pegar datos adicionales de presidente y partido
ndoc_pres <- ndoc_pres %>% 
  right_join(party_df, by = c("last_name" = "last_name")) #Cleveland has two nonconsecutive terms


# Traducir el nombre de partidos a español
ndoc_pres <- ndoc_pres %>% 
  mutate(Partido = if_else(str_detect(Party,"Democratic"), "Democrático",
                           if_else(str_detect(Party, "Republican"), "Republicano", Party))) 

#Eliminar Cleveland que esta repetido
ndoc_pres = ndoc_pres[ndoc_pres$last_name!="Cleveland (second term)",]
ndoc_pres = ndoc_pres[ndoc_pres$speaker!="Hillary Clinton",]

#Nos quedamos con top 15
top15_df <- ndoc_pres %>% 
  arrange(desc(n_docs)) %>% 
  head(15)
  
top15_df %>% 
  ggplot(aes(x = fct_reorder(last_name, n_docs), y = n_docs, fill = Partido))+
  geom_col()+
  geom_text(aes(label = n_docs), vjust = 0.5, nudge_y = 50) +
  theme_bw()+
  scale_y_continuous(breaks = pretty_breaks(n = 10))+
  scale_fill_manual(values = c("Democrático" = "#003f5c", "Republicano" = "#ff6361")) +
  labs(title = 'Número de documentos presidenciales con término "México"', 
       y = "#", 
       x = "") +
  coord_flip() +
  theme(panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank(),
        aspect.ratio = 1)

```

```{r}
top15_df
```

#### ii) Normalized by total docs by president

```{r}
ndoc_pres = inner_join(all_articles_presidents_df, ndoc_pres, by = c("president" = "speaker"))
ndoc_pres['share'] = ndoc_pres$n_docs/as.integer(ndoc_pres$records)*100

#Nos quedamos con top 15
top15_df <- ndoc_pres %>% 
  arrange(desc(share)) %>% 
  head(15)
  
top15_df %>% 
  ggplot(aes(x = fct_reorder(last_name, share), y = share, fill = Partido))+
  geom_col()+
  geom_text(aes(label = round(share,1)), vjust = 0.5, nudge_y = 1) +
  theme_bw()+
  scale_y_continuous(breaks = pretty_breaks(n = 10))+
  scale_fill_manual(values = c("Demócrata" = "#003f5c", "Republicano" = "#ff6361", "Whig" = "#ffa600")) +
  labs(title = 'Número de documentos presidenciales con término "México"', 
       subtitle = 'ponderado por total de documentos',
       y = "% del total de docs", 
       x = "") +
  coord_flip() +
  theme(panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank(),
        aspect.ratio = 1)
```

### H. Save each country's articles in different formats: CORPUS, TOKENS, N-GRAMS, DFM

To create the tokenized file, we do the following: - Tokenizing (bag of word assumption) - Discarding stop words - Removing capitalization, punctuation and numbers - Combining similar terms (lemmatizing)

```{r,warning=FALSE}
save(trade_partners_lst, file = paste0(CLEAN_DATA_PATH, "clean_articles_ALL"))

for (country in names(trade_partners_lst)){
  
  print(country)

  # Save CORPUS
  temp_corpus = corpus(trade_partners_lst[[country]], text_field = "text")
  save(temp_corpus, file = paste0(CLEAN_DATA_PATH, "corpus_", country))
  
  # Save TOKENS
  temp_tokens<- temp_corpus %>%
    tokens(split_hyphens = T,
           remove_punct = TRUE,
           remove_numbers = TRUE,
           remove_symbols = TRUE) %>%
    tokens_tolower(keep_acronyms = T) %>% # I decided to keep acronyms (govt doc!)
    tokens_remove(pattern = stopwords("en")) %>% 
    tokens_wordstem()
  save(temp_tokens, file = paste0(CLEAN_DATA_PATH, "tokens_", country))
  
  # Save N-GRAMS
  temp_tokens_ngram <- temp_corpus %>%
    tokens(split_hyphens = T,
           remove_punct = TRUE,
           remove_numbers = TRUE,
           remove_symbols = TRUE) %>%
    tokens_tolower(keep_acronyms = T) %>% # I decided to keep acronyms (govt doc!)
    tokens_remove(pattern = stopwords("en")) %>% 
    tokens_wordstem() %>% 
    tokens_ngrams(n = 2:4)
  save(temp_tokens, file = paste0(CLEAN_DATA_PATH, "tokens_ngram_", country))
  
  # Save DFM
  temp_dfm_tokens <- dfm(temp_tokens)
  save(temp_dfm_tokens, file = paste0(CLEAN_DATA_PATH, "dfm_tokens_", country))
  temp_dfm_tokens_ngram <- dfm(temp_tokens_ngram)
  save(temp_dfm_tokens_ngram, file = paste0(CLEAN_DATA_PATH, "dfm_tokens_ngram_", country))
}
```
