---
title: "cleaning_n_descriptive"
output: pdf_document
date: "2023-04-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### A. Load all relevant packages and set directories

```{r, message=FALSE, warning = FALSE}
require(quanteda)
require(quanteda.textmodels)
require(quanteda.textstats)
require(quanteda.textplots)
require(quanteda.corpora)

library(ggrepel)
library(readxl)
library(rvest)
require(readtext)
require(devtools)
require(tidyverse)
require(ggplot2) 
library(stringr)
library(purrr)
library(readr)
library(lubridate)
```

```{r, message=FALSE, warning = FALSE}
rm(list = ls())
DATA_PATH = "/Users/hugosalas/Roemer & Salas/data"
SCRIPT_PATH = "/Users/hugosalas/Roemer & Salas/"

source(str_c(SCRIPT_PATH, 'data_manipulation_utils.R'))
```

### B. Load all relevant files and DF

```{r, message=FALSE}

## Article data from our 5 countries
FILES_TO_LOAD = c("all_articles_CANADA_df", "all_articles_JAPAN_df", 
                  "all_articles_GERMANY_df", "all_articles_CHINA_df", 
                  "all_articles_MEXICO_df")

# Store all dfs in a list
trade_partners_lst = list()

for (file in FILES_TO_LOAD){
  load(str_c(DATA_PATH,'/' , file))
  
  country_name = str_replace(file, "all_articles_", "")
  country_name = str_replace(country_name, "_df", "")
  
  if (file != "all_articles_MEXICO_df"){
    trade_partners_lst[[country_name]] = country_df
    rm(country_df)
  } else {
    trade_partners_lst[[country_name]] = mexico_df
    rm(mexico_df)
  }
}

## Data at the president level with party membership, legnth of stay, among others
party_df <- read_csv(str_c(DATA_PATH, "/presidents.csv"))
```

### C. Data cleaning and manipulation

```{r, message=FALSE}
## Clean the data we have on presidents
party_df = clean_party_df(party_df)

## Cleaning our doc data from all our countries
for (country in seq_along(trade_partners_lst)){
  # Reformat dates in all DFs so that they look intuitive
  trade_partners_lst[[ country ]]$date = as.Date(as.numeric(trade_partners_lst[[ country ]]$date))
  # Add last name and year to DF
  trade_partners_lst[[ country ]] = add_last_name_n_year_to_df( trade_partners_lst[[ country ]] )
  # Merge with party/president data
  trade_partners_lst[[ country ]] <- trade_partners_lst[[ country ]] %>% 
    left_join(party_df, by = c("last_name" = "last_name"))
  # Recategorize party variable so it separates between democrats and republicans
  trade_partners_lst[[ country ]] <- recategorize_parties(trade_partners_lst[[ country ]])
}
```

### D. Quick data exploration to get some truths

```{r, message=FALSE}
for (country in names(trade_partners_lst)){
  print(str_c('############## ', country, ' ############'))
  
  nrows = nrow( trade_partners_lst[[ country ]] )
  print(str_c('Number of rows/docs: ', nrows ))
  
  print('Party Membership %')
  print(table( trade_partners_lst[[ country ]]$Party)/nrows*100)
  
  print('Doc category % (top 7)')
  print(sort(colSums( trade_partners_lst[[ country ]][,5:74], na.rm = TRUE), decreasing = TRUE)[1:7]/nrows)
  
  print(str_c('Share of docs not coming directly from the president: ', sum(is.na(trade_partners_lst[[ country ]]$Party))/nrows*100))
  
  for (i in 1:3){
    cat("\n")
  }
}
```
### E. Mentions by year per country

```{r, warning=FALSE}
counts_year = data.frame()

for (country in seq_along(trade_partners_lst)){
  
  # Group by year while we count
  groupby_temp <- trade_partners_lst[[country]]%>% 
    group_by(year) %>% 
     summarise(n_docs = n())
  
  # Add a column to identify each batch/country
  groupby_temp['country'] = names(trade_partners_lst)[country]
  
  # Append to df
  counts_year = rbind(counts_year, groupby_temp)
}


# Since there wasn't much happening before 1900, let's create several graphs 
#   with varying start years
for (start_year in c(1800,1900, 1950, 1980)){
  plot = ggplot(counts_year[counts_year['year']>start_year,], aes(year, n_docs, color = country)) + 
    geom_line(aes(group=country)) +
    theme_test()+
    scale_x_continuous(breaks = pretty_breaks(n = 10))+
    scale_y_continuous(breaks = pretty_breaks(n = 5))+
    theme(axis.text.x = element_text(angle = 0, vjust = .7))+
    labs(title = '" ',
         subtitle = "",
         y = "", 
         x = "", 
         caption = "",
         color = 'Legend')
  
  print(plot)
}

```

### Number of drug-related documents by president 

```{r}
ndoc_pres <- usmex_df %>% 
  group_by(last_name) %>% 
  summarise(n_docs = n()) %>% 
  arrange(desc(n_docs)) 
 #Trump es el unico en top10 que solo fungio un termino; en realidad deberia estandarizar por eso

ndoc_pres <- ndoc_pres %>% 
  right_join(party, by = c("last_name" = "last_name")) #Cleveland has two nonconsecutive terms
                                             # there are two adams presidents (do same as roosevelt above)

 
 ndoc_pres <- ndoc_pres[-5,] #eliminar Johnson repetido
 ndoc_pres <- ndoc_pres[-14,] #eliminar Cleveland repetido
 
ndoc_pres <- ndoc_pres %>% 
  mutate(Partido = if_else(str_detect(Party,"Democratic"), "Democrático",
                           if_else(str_detect(Party, "Republican"), "Republicano", Party))) 
  
ndoc_top15 <- ndoc_pres %>% 
  arrange(desc(n_docs)) %>% 
  head(15)
  
  ndoc_top15 %>% 
  ggplot(aes(x = fct_reorder(last_name, n_docs), y = n_docs, fill = Partido))+
  geom_col()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, vjust = .7))+
  scale_fill_manual(values = wesanderson::wes_palette("Moonrise3", n = 3))+
    scale_y_continuous(breaks = seq(0, max(ndoc_top15$n_docs), by = 50))+
  labs(title = 'Número de discursos y entrevistas presidenciales con término "México"', 
       y = "Número de Documentos", 
       x = "")

```

1. Normalizar por numero de dias en el poder

```{r}
  ndoc_pres %>% 
  mutate(ndocsXday = n_docs/duration) %>% arrange(desc(ndocsXday)) %>% 
  head(15) %>% 
  ggplot(aes(x = fct_reorder(last_name, ndocsXday), y = ndocsXday, fill = Partido))+
  geom_col()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, vjust = .7))+
  scale_fill_manual(values = wesanderson::wes_palette("Moonrise3", n = 3))+
  scale_y_continuous(breaks = seq(0, .5, by = 0.05))+
  labs(title = 'Discursos y entrevistas presidenciales con mención de "México" ',
       subtitle = "ponderado por número días en la presidencia",
       y = "Número de Documentos por día", 
       x = "")
```

2. Normalizar por total de discursos (en cuantos discursos usan el termino  Mexico como porcentaje de su numero total de discursos)

```{r}
######  total de discursos por presidente: 
base_url <- "https://www.presidency.ucsb.edu/advanced-search?field-keywords=&field-keywords2=&field-keywords3=&from%5Bdate%5D=&to%5Bdate%5D=&person2="

person_ids <- 200257:200320

links <- paste0(base_url, person_ids, "&category2%5B%5D=406&category2%5B%5D=74&category2%5B%5D=53&category2%5B%5D=46&category2%5B%5D=45&items_per_page=25")

# Create an empty data frame to store the results
results_df <- data.frame(president = character(), records = numeric())

# Loop through each link and scrape the relevant information
for (link in links) {
  page <- read_html(link)
  
  # Extract the president's name from the page and remove the newline character
  president <- page %>% html_nodes(".odd .views-field-field-docs-person") %>% html_text() %>% gsub("\n", "", .)
  president <- president[1]
  
  # Extract the number of records found from the page and remove any non-numeric characters
  records <- page %>% html_node("#block-system-main h3") %>% html_text() %>% gsub("[^0-9]", "", .)
  
  # Convert records to numeric format if possible
  if (!is.na(records) & nchar(records) > 0) {
    records <- as.numeric(records)
    
    # Remove the 125 if it appears before the number of records
    if (!is.na(records) & is.numeric(records) & substr(records, 1, 3) == "125") {
      records <- substr(records, 4, nchar(records))
    }
  }
  
  # Check if president and records are not empty before adding to the data frame
  if (!is.na(president) & !is.na(records) & president != "" & records != "") {
    # Add the results to the data frame
    results_df <- rbind(results_df, data.frame(president = president, records = records))
  }
}

# View the final results
results_df

```

Now I must match the total number of records with our other dataframes, using the presidents' names. 

```{r, warning= FALSE}
#eliminate white space (aquí me quedé 28 abril)
results_df <- results_df %>% 
  mutate(president = gsub("^\\s+|\\s+$", "", president))


#results_df$president
#usmex_df$speaker

usmex_df<- usmex_df %>% 
  filter(!is.na(text)) %>% 
  full_join(results_df, by = c("speaker" = "president"), multiple = "all") %>% 
  filter(!(is.na(date)))

```



```{r}

ndoc_pres_weighted <- usmex_df %>% 
  group_by(last_name) %>% 
  summarise(n_docs = n(),
            total_speeches = as.numeric(records),
            ndoc_prop = n_docs/total_speeches*100,
            Partido = Party, 
            year_office = year(took_office)) %>% 
  slice(1) %>% 
  arrange(desc(ndoc_prop)) #Andrew Johnson, Polk, Trump en ese orden (poner numeros)

#on Johnson:  https://millercenter.org/president/johnson/foreign-affairs 
#https://onlinelibrary.wiley.com/doi/abs/10.1002/9781118607879.ch5 
# https://muse.jhu.edu/article/419283 ** Romero describe a Johnson 
# https://www.redalyc.org/journal/600/60059441004/html/ **

top3 <- ndoc_pres_weighted %>%
  filter(last_name == "Johnson" | last_name == "Polk" | last_name == "Trump")


ndoc_pres_weighted %>%   
head(15) %>% 
ggplot(aes(x = fct_reorder(last_name, ndoc_prop), y = ndoc_prop, fill = Partido))+
  geom_col()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, vjust = .7))+
  scale_fill_manual(values = wesanderson::wes_palette("Moonrise3", n = 4))+
  labs(title = 'Documentos presidenciales con mención de "México" ',
       subtitle = "ponderado por total de discursos",
       y = "%", 
       x = "", caption = "*discursos disponibles en https://www.presidency.ucsb.edu/") +
 geom_label_repel(data = top3, aes(x = last_name, 
                             y = ndoc_prop - 1, label = year_office, hjust = 1), 
                 size = 3, nudge_x = -2, nudge_y = 1) +
  guides(
  fill = guide_legend(
    title = "Partido",
    override.aes = aes(label = "")
  )
)
```

### Discursos por ano que mencionan Mexico

opciones: hacerlo como valor absoluto... recortarlo a partir de 1945... hacerlo como proporcion
combinacion de las anteriores
creo que tiene mas sentido como proporcion

```{r, warning=FALSE}
ndoc_year <- usmex_df%>% 
  group_by(year) %>% 
   summarise(n_docs = n(),
            total_speeches = as.numeric(records),
            ndoc_prop = n_docs/total_speeches*100,
            Partido = Party, 
            year_office = year(took_office)) %>% 
  slice(1) 

save(ndoc_year, file = "ndoc_year.RData")

ndoc_year %>% arrange(desc(ndoc_prop)) %>% head(10)


ndoc_year %>% 
  ggplot(aes(x = year, y = ndoc_prop))+
  geom_line()+
  theme_test()+
  scale_x_continuous(breaks = seq(1800,2023,10))+
  scale_y_continuous(breaks = seq(0,11,0.7))+
  theme(axis.text.x = element_text(angle = 45, vjust = .7))+
  # agregar vlines en fechas relevantes (revision historica)
  geom_vline(aes(xintercept = 1847.5), linetype = "dotted", color = "blue")+   
  annotate("text", x=1827, y=10, label="1848 - Fin de Guerra \nMéxico-Americana ", color = "blue", size = 3)+
  geom_vline(aes(xintercept = 1864), linetype = "dotted", color = "blue")+   
  annotate("text", x=1872, y=4.0, label="1862 - \n                         Maximiliano en México", color = "blue", size = 3)+
  geom_vline(aes(xintercept = 1923), linetype = "dotted", color = "blue") +   
  annotate("text", x=1937, y=3.7, label="1923 - \nSuspensión \nde relaciones \ndiplomáticas", color = "blue", size = 3) +
  geom_vline(aes(xintercept = 1993), linetype = "dotted", color = "blue") +   
  annotate("text", x=1985, y=3.0, label="1993 - \nTLCAN", color = "blue", size = 3) +
  geom_vline(aes(xintercept = 2017), linetype = "dotted", color = "blue") +   
  annotate("text", x=2010, y=5.0, label="2017 - \nTrump", color = "blue", size = 3)+
  labs(title = 'Documentos presidenciales con mención de "México" ',
       subtitle = "ponderado por total de discursos",
       y = "%", 
       x = "", caption = "*discursos disponibles en https://www.presidency.ucsb.edu/")
```

## Converting dataframe to corpus

```{r,warning=FALSE}
corpus_usmex <- corpus(usmex_df, text_field = "text")
save(corpus_usmex,file = "data/corpus_usmex")
#summary(corpus_usmex)
class(corpus_usmex)
#as.character(corpus_usmex)[300]
```

## Subsetting 

I decide to create different corpora, in case I may need them further down. 

```{r}
post_1900 <- corpus_usmex %>% 
  corpus_subset(year >= 1900)
save(post_1900,file = "data/corpus_post1900")


Trump_Biden <- corpus_usmex %>% 
  corpus_subset(last_name %in% c("Trump", "Biden"))
save(Trump_Biden,file = "data/corpus_TrumpBiden")

republicans <- corpus_usmex %>% 
  corpus_subset(Party == "Republican")
save(republicans,file = "data/corpus_republicans")

democratic <- corpus_usmex %>% 
  corpus_subset(Party == "Democratic")
save(democratic,file = "data/corpus_democratic")
```


Pico 1923: 


La suspensión de relaciones diplomáticas entre México y Estados Unidos en 1923 se debió en gran medida a las tensiones que surgieron después de la Revolución Mexicana y la posterior promulgación de la Constitución Mexicana de 1917, que estableció reformas agrarias y laborales radicales.

Además, durante el gobierno del presidente mexicano Álvaro Obregón (1920-1924), México se vio envuelto en una serie de conflictos con empresas estadounidenses, incluida la compañía petrolera estadounidense Standard Oil, que había sido expropiada por el gobierno mexicano en 1917. Esto llevó a la aplicación de sanciones comerciales por parte de Estados Unidos y a un aumento de las tensiones diplomáticas.

En 1923, las tensiones alcanzaron un punto crítico cuando el embajador de Estados Unidos en México, Dwight Morrow, fue expulsado del país después de criticar al gobierno mexicano en un discurso público. A su vez, el presidente de Estados Unidos, Calvin Coolidge, ordenó la retirada de todos los diplomáticos estadounidenses de México y la suspensión de relaciones diplomáticas con el país.

Las relaciones diplomáticas no se restablecieron hasta 1928, cuando el presidente mexicano Plutarco Elías Calles y el presidente estadounidense Herbert Hoover firmaron un acuerdo para normalizar las relaciones entre los dos países.



## Preprocessing

 - Tokenizing (bag of word assumption)
 - Discarding stop words
 - Removing capitalization, punctuation and numbers
 - Combining similar terms (lemmatizing)

```{r}
toks_usmex<- corpus_usmex %>%
  tokens(split_hyphens = T,
         remove_punct = TRUE,
         remove_numbers = TRUE,
         remove_symbols = TRUE) %>%
  tokens_tolower(keep_acronyms = T) %>% # I decided to keep acronyms (govt doc!)
  tokens_remove(pattern = stopwords("en")) %>% 
  tokens_wordstem()

#head(toks_usmex)
```

Let's look at how our tokenized corpus would look with different n-grams. 
```{r}
toks_ngram <- corp_drug_speeches %>%
  tokens(split_hyphens = T,
         remove_punct = TRUE,
         remove_numbers = TRUE,
         remove_symbols = TRUE) %>%
  tokens_tolower(keep_acronyms = T) %>% # I decided to keep acronyms (govt doc!)
  tokens_remove(pattern = stopwords("en")) %>% 
  tokens_wordstem() %>% 
  tokens_ngrams(n = 2:4)

#head(toks_ngram)
```


## Creating Document Feature Matrix (DTM)
```{r}
dtm_drugs <- dfm(toks_drugs)
dtm_drugs_ngram <- dfm(toks_ngram)
```

### Exploring our DTM

```{r}
ndoc(dtm_drugs)
nfeat(dtm_drugs)

#document length 
by_docs <- rowSums(dtm_drugs)

#top features
topfeatures(dtm_drugs, n = 200)

dtm_drugs_weight <- dfm_weight(dtm_drugs, scheme = "prop")
#dtm_drugs_weight
```

### save corpora

```{r}
save(toks_drugs, file = "data/toks_drugs")
save(toks_ngram, file = "data/toks_ngram")
save(dtm_drugs_ngram, file = "data/dtm_drugs_ngram")
save(dtm_drugs, file = "data/dtm_drugs")
save(drugs_df, file = "data/drug_speeches")
save(party, file = "data/party")
save(total_speeches, file = "data/total_speeches")
```
